---
output:
  word_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.width=15,fig.height=12)

library(lmerTest)
library(ggplot2)
library(data.table)
library(cowplot)

```

```{r}
######Loading and Processing Data######


#Loading data
data<-read.csv("Human Data/Processed Data/DGS Data L PROCESSED 20230420 2308.csv")

#Melt a dataframe for analyzing positive choices
posData<-melt(as.data.table(data),
               id.vars=c(1,3,6:10,49:58,67:71),
               measure.vars=59:63)

#Rename variable and value columns
colnames(posData)[23:24]<-c("trait","choice")

#Relabel levels of trait variable
posData$trait<-factor(posData$trait,labels=c("artistic",
                                             "healthy",
                                             "kind",
                                             "sexy",
                                             "wealthy"))


#Melt a dataframe for analyzing negative choices
negData<-melt(as.data.table(data),
               id.vars=c(1,3,6:10,49:58,67:71),
               measure.vars=64:66)

#Rename variable and value columns
colnames(negData)[23:24]<-c("domain","choice")

#Relabel levels of trait variable
negData$domain<-factor(negData$domain,labels=c("moral",
                                             "pathogen",
                                             "sex"))

#Convert necessary variables to factors
posData[,c(1:3,5,7)]<-lapply(posData[,c(1:3,5,7)],as.factor)
negData[,c(1:3,5,7)]<-lapply(negData[,c(1:3,5,7)],as.factor)

```



```{r}

######Analyses######


#Positive Traits#

#Do the sexes differ in which traits they reveal?
posReg1<-aov(choice~trait*sex+Error(PIN),data=posData)

#Does this differ by country?
posReg2<-aov(choice~trait*sex+trait*country+Error(PIN),data=posData)

#Does this differ by sexual orientation?
posReg3<-aov(choice~trait*sex*kinsey+Error(PIN),data=posData)


#Control analyses
#Relationship status:
posReg4<-aov(choice~trait*sex+
               relstat+
               Error(PIN),data=posData)

#Disgust sensitivity:
posReg5<-aov(choice~trait*sex+
               tddMoral+tddPath+tddSex+
               Error(PIN),data=posData)

#Preferences
posReg6<-aov(choice~trait*sex+
               idealArt+idealHealth+idealKind+idealSexy+idealResources+
               Error(PIN),data=posData)

#Own traits
posReg6<-aov(choice~trait*sex+
               selfArt+selfHealth+selfKind+selfSexy+selfResources+
               Error(PIN),data=posData)

#MV
posReg7<-aov(choice~trait*sex+
               mv+
               Error(PIN),data=posData)



#Choices by own traits for positive traits
artReg<-lm(choiceArt~
             selfArt+
             selfHealth+
             selfKind+
             selfSexy+
             selfResources,
           data=data)

healthReg<-lm(choiceHealth~
             selfArt+
             selfHealth+
             selfKind+
             selfSexy+
             selfResources,
           data=data)

kindReg<-lm(choiceKind~
             selfArt+
             selfHealth+
             selfKind+
             selfSexy+
             selfResources,
           data=data)

sexyReg<-lm(choiceSexy~
             selfArt+
             selfHealth+
             selfKind+
             selfSexy+
             selfResources,
           data=data)

#Own traits by choices
resourcesReg<-lm(choiceWealthy~
             selfArt+
             selfHealth+
             selfKind+
             selfSexy+
             selfResources,
           data=data)



#Disgusting Traits#

#Do the sexes differ in which traits they reveal?
negReg1<-aov(choice~domain*sex+Error(PIN),data=negData)

#Does this differ by country?
negReg2<-aov(choice~domain*sex+domain*country+Error(PIN),data=negData)

#Does this differ by sexual orientation?
negReg3<-aov(choice~domain*sex+domain*kinsey+Error(PIN),data=negData)


#Control analyses
#Relationship status:
negReg4<-aov(choice~domain*sex+
               relstat+
               Error(PIN),data=negData)

#Disgust sensitivity:
negReg5<-aov(choice~domain*sex+
               tddMoral+tddPath+tddSex+
               Error(PIN),data=negData)

#Preferences
negReg6<-aov(choice~domain*sex+
               idealArt+idealHealth+idealKind+idealSexy+idealResources+
               Error(PIN),data=negData)

#Own domains
negReg6<-aov(choice~domain*sex+
               selfArt+selfHealth+selfKind+selfSexy+selfResources+
               Error(PIN),data=negData)

#MV
negReg7<-aov(choice~domain*sex+
               mv+
               Error(PIN),data=negData)




#Choices by disgust senstivity for disgusting traits
moralReg<-lm(choiceMoral~
               tddMoral+
               tddPath+
               tddSex,
             data=data)

pathReg<-lm(choicePath~
               tddMoral+
               tddPath+
               tddSex,
             data=data)

sexReg<-lm(choiceSex~
               tddMoral+
               tddPath+
               tddSex,
             data=data)



#Load in pre-ratings of digust items
disRat<-read.csv("Human Data/Processed Data/DGS Disgust Items.csv")

#Create a dataframe for analysis
disgustItems<-data.frame("sex"=rep(c(0,1),each=6*3),
                         "domain"=rep(c("pathogen","sex","moral"),each=6),
                         "item"=rep(1:6,times=3))

#Compute average disgust rating at the item level
disgustItems$rating<-c(colMeans(disRat[disRat$Sex=="Female",-1]),
                       colMeans(disRat[disRat$Sex=="Male",-1]))

#Determine the number of times each item was chosen
disgustItems$choice<-c(sapply(c("pathogen","sex","moral"),function(x) sapply(1:6,function(y) sum(data[data$sex==0,y+21]==x))),
                       sapply(c("pathogen","sex","moral"),function(x) sapply(1:6,function(y) sum(data[data$sex==1,y+21]==x))))

#How disgusting an item was did not predict how frequently it was chosen
disgustRatingReg<-lm(choice~rating*domain*sex,data=disgustItems)


#Repeat the above but collapsing by sex because it had no significant effects:

#Create a dataframe for analysis
disgustItemsNS<-data.frame("domain"=rep(c("pathogen","sex","moral"),each=6),
                         "item"=rep(1:6,times=3))

#Compute average disgust rating at the item level
disgustItemsNS$rating<-colMeans(disRat[,-1])

#Determine the number of times each item was chosen
disgustItemsNS$choice<-c(sapply(c("pathogen","sex","moral"),function(x) sapply(1:6,function(y) sum(data[,y+21]==x))))

#How disgusting an item was did not predict how frequently it was chosen
disgustRatingReg<-lm(choice~rating+domain,data=disgustItemsNS)

```



```{r}
######Plots######


###Positive Traits###

#Choices by Trait and Sex#

#Plot average choice by trait and sex for positive traits
posPlot<-qplot(trait,choice,fill=sex,data=posData,
               xlab="Trait",
               ylab="Number of Times Chosen",
               geom="blank")+
  scale_x_discrete(labels=tools::toTitleCase(levels(posData$trait)))+
  geom_bar(stat="summary",fun="mean",position="dodge")+
  theme_gray(base_size=40)+
  scale_fill_discrete(name="Sex",labels=c("Female","Male"))+
  geom_errorbar(stat="summary",fun.data="mean_cl_boot",position="dodge")+
  geom_jitter(alpha=.1,shape=21,height=.1)



#Create a categorical sexual orientation variable based on Kinsey scores
posData$sexOrient<-ifelse(posData$kinsey<2,"Heterosexual",
                          ifelse(posData$kinsey>4,"Gay/Lesbian","Bisexual"))

posData$sexOrient<-factor(posData$sexOrient,levels=c("Heterosexual",
                                                     "Bisexual",
                                                     "Gay/Lesbian"))



posData$country<-factor(posData$country,labels=c("Poland","U.S."),levels=c("pl","en"))

#Plot average choice by trait and sex for positive traits
posPlotCountry<-qplot(trait,choice,fill=sex,data=posData,
               xlab="Trait",
               ylab="Number of Times Chosen",
               geom="blank")+
  scale_x_discrete(labels=tools::toTitleCase(levels(posData$trait)))+
  geom_bar(stat="summary",fun="mean",position="dodge")+
  theme_gray(base_size=30)+
  scale_fill_discrete(name="Sex",labels=c("Female","Male"))+
  geom_errorbar(stat="summary",fun.data="mean_cl_boot",position="dodge")+
  geom_jitter(alpha=.1,shape=21,height=.1)+
  facet_wrap(~country)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))



#Plot average choice by trait and sex for positive traits
posPlotSO<-qplot(trait,choice,fill=sex,data=posData,
               xlab="Trait",
               ylab="Number of Times Chosen",
               geom="blank")+
  scale_x_discrete(labels=tools::toTitleCase(levels(posData$trait)))+
  geom_bar(stat="summary",fun="mean",position="dodge")+
  theme_gray(base_size=30)+
  scale_fill_discrete(name="Sex",labels=c("Female","Male"))+
  geom_errorbar(stat="summary",fun.data="mean_cl_boot",position="dodge")+
  geom_jitter(alpha=.1,shape=21,height=.1)+
  facet_wrap(~sexOrient)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))



#Choices by Own Trait#

#Frequency of choosing artistic options as a function of own artistic ability
artPlot<-qplot(selfArt,choiceArt,data=data,
      xlab="Artistic Ability (Self)",
      ylab="Artistic Ability Option\n(# of Times Chosen)",
      geom="blank")+
  geom_smooth(method="lm")+
  theme_gray(base_size=30)+
  geom_jitter()


#Frequency of choosing kindness options as a function of own kindness
kindPlot<-qplot(selfKind,choiceKind,data=data,
      xlab="Kindness (Self)",
      ylab="Kindness Option\n(# of  Times Chosen)",
      geom="blank")+
  geom_smooth(method="lm")+
  theme_gray(base_size=30)+
  geom_jitter()


#Frequency of choosing sexiness options as a function of own sexiness
sexyPlot<-qplot(selfSexy,choiceSexy,data=data,
      xlab="Sexiness (Self)",
      ylab="Sexiness Option\n(# of  Times Chosen)",
      geom="blank")+
  geom_smooth(method="lm")+
  theme_gray(base_size=30)+
  geom_jitter()






###Disgusting Traits###

#Choices by Trait and Sex#

#Plot average choice by trait and sex for positive traits
negPlot<-qplot(domain,choice,fill=sex,data=negData,
               xlab="Domain",
               ylab="Number of Times Chosen",
               geom="blank")+
  scale_x_discrete(labels=tools::toTitleCase(levels(negData$domain)))+
  geom_bar(stat="summary",fun="mean",position="dodge")+
  theme_gray(base_size=40)+
  scale_fill_discrete(name="Sex",labels=c("Female","Male"))+
  geom_errorbar(stat="summary",fun.data="mean_cl_boot",position="dodge")+
  geom_jitter(alpha=.1,shape=21,height=.1)



negData$country<-factor(negData$country,labels=c("Poland","U.S."),levels=c("pl","en"))
levels(negData$country)<-c("Poland","U.S.")

#Plot average choice by domain and sex for negitive domains
negPlotCountry<-qplot(domain,choice,fill=sex,data=negData,
               xlab="Domain",
               ylab="Number of Times Chosen",
               geom="blank")+
  scale_x_discrete(labels=tools::toTitleCase(levels(negData$domain)))+
  geom_bar(stat="summary",fun="mean",position="dodge")+
  theme_gray(base_size=30)+
  scale_fill_discrete(name="Sex",labels=c("Female","Male"))+
  geom_errorbar(stat="summary",fun.data="mean_cl_boot",position="dodge")+
  geom_jitter(alpha=.1,shape=21,height=.1)+
  facet_wrap(~country)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))



#Create a categorical sexual orientation variable based on kinsey scores
negData$sexOrient<-ifelse(negData$kinsey<2,"Heterosexual",
                          ifelse(negData$kinsey>4,"Gay/Lesbian","Bisexual"))

negData$sexOrient<-factor(negData$sexOrient,levels=c("Heterosexual",
                                                     "Bisexual",
                                                     "Gay/Lesbian"))

#Plot average choice by trait and sex for positive traits
negPlotSO<-qplot(domain,choice,fill=sex,data=negData,
               xlab="Domain",
               ylab="Number of Times Chosen",
               geom="blank")+
  scale_x_discrete(labels=tools::toTitleCase(levels(negData$domain)))+
  geom_bar(stat="summary",fun="mean",position="dodge")+
  theme_gray(base_size=30)+
  scale_fill_discrete(name="Sex",labels=c("Female","Male"))+
  geom_errorbar(stat="summary",fun.data="mean_cl_boot",position="dodge")+
  geom_jitter(alpha=.1,shape=21,height=.1)+
  facet_wrap(~sexOrient)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))



#Choices by Own Disgust Sensitivity#

#Frequency of choosing moral options as a function of moral disgust sensitivity
moralPlot<-qplot(tddMoral,choiceMoral,data=data,
      xlab="Moral Disgust Sensitivity",
      ylab="Morally Disgusting Option\n(# of  Times Chosen)",
      geom="blank")+
  geom_smooth(method="lm")+
  theme_gray(base_size=30)+
  geom_jitter()


#Frequency of choosing pathogen options as a function of pathogen disgust sensitivity
pathPlot<-qplot(tddPath,choicePath,data=data,
      xlab="Pathogen Disgust Sensitivity",
      ylab="Pathogenically Disgusting Option\n(# of  Times Chosen)",
      geom="blank")+
  geom_smooth(method="lm")+
  theme_gray(base_size=30)+
  geom_jitter()


#Frequency of choosing pathogen options as a function of pathogen disgust sensitivity
sexPlot<-qplot(tddSex,choiceSex,data=data,
      xlab="Sexual Disgust Sensitivity",
      ylab="Sexually Disgusting Option\n(# of  Times Chosen)",
      geom="blank")+
  geom_smooth(method="lm")+
  theme_gray(base_size=30)+
  geom_jitter()


negChoicePlot<-qplot(rating,choice,data=disgustItems,
                     xlab="Item Disgust Rating",ylab="Frequency of Item Choice")+
  geom_smooth(method="lm")+
  theme_gray(base_size=30)

```

<br>
<br>
  
## Do Negative Information Choices Depend on Doman and Sex?
<br>
Yes.  
<br>
Disgust domain and sex interact to predict choices in the dating game, *F*(`r unlist(summary(negReg1))[12]`,`r unlist(summary(negReg1))[13]`) = `r round(unlist(summary(negReg1))[21],2)`, *p* = `r ifelse(unlist(summary(negReg1))[24]<.001,"p<.001",round(unlist(summary(negReg1))[24],3))`.

Controlling for relationship status, disgust senstivity, preferences, own traits, or mate value did not affect this interaction.

```{r, out.width="75%",out.height="75%"} 
summary(negReg1)
negPlot 
```

<br>
<br>

### Does this differ by country?

<br>
Not really.
<br>
Disgust domain and country interact to predict choices in the dating game, *F*(`r unlist(summary(negReg2))[18]`,`r unlist(summary(negReg2))[19]`) = `r round(unlist(summary(negReg2))[30],2)`, *p* = `r ifelse(unlist(summary(negReg2))[34]<.001,"p<.001",round(unlist(summary(negReg2))[34],3))`

However, the three-way interaction between disgust domain, country, and sex was not significant.

```{r} 
summary(negReg2)
negPlotCountry
```

<br>
<br>

### Does this differ by sexual orientation?

<br>
Not really.
<br>
Disgust domain and Kinsey score to predict choices in the dating game, *F*(`r unlist(summary(negReg3))[18]`,`r unlist(summary(negReg3))[19]`) = `r round(unlist(summary(negReg3))[30],2)`, *p* = `r ifelse(unlist(summary(negReg3))[34]<.001,"p<.001",round(unlist(summary(negReg3))[34],3))`

However, the three-way interaction between disgust domain, sexual orientation, and sex was not significant.

```{r} 
summary(negReg3)
negPlotSO
```

<br>
<br>

### Does disgust sensitivity predict game choices?

<br>

Yes.
<br>

For all domains, greater disgust sensitivity predicts less frequently choosing that domain

<br>

Moral Disgust Sensitivity:
```{r}
summary(moralReg)
```

<br>

Pathogen Disgust Sensitivity:
```{r}
summary(pathReg)
```

<br>

Sexual Disgust Sensitivity:
```{r}
summary(sexReg)
```

<br>

```{r,fig.height=25}
plot_grid(moralPlot,pathPlot,sexPlot,nrow=3)
```

<br>
<br>


## Do Positive Information Choices Depend on Doman and Sex?

<br>
Yes.  
<br>
Trait and sex interact to predict choices in the dating game, *F*(`r unlist(summary(posReg1))[12]`,`r unlist(summary(posReg1))[13]`) = `r round(unlist(summary(posReg1))[21],2)`, *p* = `r ifelse(unlist(summary(posReg1))[24]<.001,"p<.001",round(unlist(summary(posReg1))[24],3))`

Controlling for relationship status, disgust senstivity, preferences, own traits, or mate value did not affect this interaction.

```{r,out.width="75%",out.height="75%"} 
summary(posReg1)
posPlot 
```

<br>
<br>

### Does this differ by country?

<br>
Not really.
<br>
Trait and country interact to predict choices in the dating game, *F*(`r unlist(summary(posReg2))[18]`,`r unlist(summary(posReg2))[19]`) = `r round(unlist(summary(posReg2))[30],2)`, *p* = `r ifelse(unlist(summary(posReg2))[34]<.001,"p<.001",round(unlist(summary(posReg2))[34],3))`

However, the three-way interaction between trait, country, and sex was not significant.

```{r} 
summary(posReg2)
posPlotCountry
```

<br>
<br>

### Does this differ by sexual orientation?

<br>
Yes
<br>
Trait, Kinsey score, and sex interacted to predict choices in the dating game, *F*(`r unlist(summary(posReg3))[24]`,`r unlist(summary(posReg3))[25]`) = `r round(unlist(summary(posReg3))[39],2)`, *p* = `r ifelse(unlist(summary(posReg3))[44]<.001,"p<.001",round(unlist(summary(posReg3))[44],3))`


```{r} 
summary(posReg3)
posPlotSO
```

<br>
<br>

### Do own traits predict the traits chosen?

<br>

For some.

<br>

People who rated themselves higher in artistic ability (*b* = `r summary(artReg)$coefficients[2,1]`, *p* = `r ifelse(summary(artReg)$coefficients[2,4]<.001,"p<.001",round(summary(artReg)$coefficients[2,4],3))`) or sexiness (*b* = `r summary(sexyReg)$coefficients[5,1]`, *p* = `r ifelse(summary(sexyReg)$coefficients[5,4]<.001,"p<.001",round(summary(sexyReg)$coefficients[5,4],3))`) were more likely to choose these traits. However, people who rated themselves higher in kindness were *less* likely to choose kindness options (*b* = `r summary(kindReg)$coefficients[4,1]`, *p* = `r ifelse(summary(kindReg)$coefficients[4,4]<.001,"p<.001",round(summary(kindReg)$coefficients[4,4],3))`). However, this does not replicate with the more conservative exclusion criteria.

<br>

Artistic ability:
```{r}
summary(artReg)
```

<br>

Sexiness:
```{r}
summary(sexyReg)
```

<br>

Kindness:
```{r}
summary(kindReg)
```

<br>

```{r,fig.height=25}
plot_grid(artPlot,sexyPlot,kindPlot,nrow=3)
```

